### 2013-02-28 patchy-selection-paper.tex
WorkingWiki importation

>>>>

\plr{Notes for clarification.}
We can calculate the rate of ``core'' establishment, i.e.\ the mean number of reproductive events that lead to establishment as defined below, in two ways:
\begin{align}
  (\mbox{rate of establishment}) &= (\mbox{outflux of BPs from old patch}) \times (\mbox{\# estab events per BP}) \\
    \begin{split} &= (\mbox{outflux of BPs from old patch}) \times (\mbox{prob of estab of a distant BP}) \\
  & \qquad \qquad \times (\mbox{\# estab events per successful BP}) \end{split} \\
  \begin{split} &= (\mbox{subcritical occupation density}) \times \rho \times (\mbox{\# offspring per subcritical indiv}) \\
    & \qquad \qquad \times (\mbox{prob of estab in the patch}) . \end{split} 
\end{align}
The probability of establishment of a branching process is in equation~\eqref{eqn:bp_prob_estab};
the subcritical occupation density is in equation~\eqref{eqn:eqfreq}, up to a constant $C$ depending on geometry;
the number of (extra) offspring per subcritical individual is $s_B+s_m$;
and the probability of establishment in the patch is $2s_B/\xi^2$.
The ``outflux of branching processes'' we have not computed;
but we know that the probability a branching process arrives at the patch is given by equation~\eqref{eqn:estab_prob};
if it does it is present in $\mu_K$ copies, each of which leave a total of $1/s_m$ offspring; 
so equating ($\rho$ times equation~\eqref{eqn:eqfreq}) and (outflux times $\mu_K/s_m$ times equation~\eqref{eqn:estab_prob})
we have that the effective outflux (at the edge of the already occupied patch!) is 
\begin{align}
  (\mbox{outflux of BPs from old patch}) = C \rho s_m ,
\end{align}
rather than $C\rho$ which we might have guessed.
The number of establishment events per BP is as follows, in averages: 
with prob $1/\mu_K \exp(-\sqrt{\alpha} x/ \sigma)$ a total of $\mu_K$ indivs arrive at the new patch; 
each produce $1/s_m$ total core offspring;
each of these produce $s_B+s_m$ extra offspring which each have chance $2s_B/\xi^2$ of establishing,
i.e.
\begin{align}
  (\mbox{\# estab events per BP}) = \frac{(s_B+s_m) 2 s_B }{ s_m \xi^2 } \exp\left(-\frac{\sqrt{\alpha} x}{\sigma}\right) .
\end{align}
\textbf{Now} note that what we \textbf{actually} want to compute is not this rate, but rather 
\begin{align}
  \migrate &= (\mbox{outflux of BPs from old patch}) \times (\mbox{prob of estab of a distant BP}) \\
  &= C \rho s_m \times \frac{2 s_b}{\xi^2} \exp\left(- \frac{\sqrt{\alpha}x}{\sigma} \right) .
\end{align}
Finally, combining these, we can also compute that
\begin{align}
  (\mbox{\# estab events per successful BP}) = \frac{s_B+s_m}{s_m} .
\end{align}
\plr{end of notes}
